---
title: "cereal_tidytues"
author: "Meriah DeJoseph"
date: "12/10/2020"
output: html_document
---
## Doing assignment for TT group, giving myself 30 min again

##Load libraries and data
```{r}
library(tidytuesdayR)
library(ggplot2)
library(gridExtra)
library(dplyr)
library(tidyverse)
library(broom)
library(emmeans)
library(readr)
library(readxl)

cereal <- read_excel("data/cereal.xlsx")

```

# 2. Which cereal has the most and least surgar per serving? The most and least calories? The most and least protein? (and any other nutritional info you're interested in)
```{r}

maxsugar <- cereal %>% 
    filter(sugars == max(sugars)) %>% # filter to keep row where sugars is maximum
    select(name) # select column 
maxsugar
#1 Golden Crisp
#2 Smacks 

minsugar <- cereal %>% 
    filter(sugars == min(sugars, na.rm=T)) %>% 
    select(name) 
minsugar
#saw that quaker is -1 so I'm going to remove these values and rerun
cereal[cereal == -1] <- NA
# 1 All-Bran with Extra Fiber
# 2 Cream of Wheat (Quick)   
# 3 Puffed Rice              
# 4 Puffed Wheat             
# 5 Shredded Wheat           
# 6 Shredded Wheat 'n'Bran   
# 7 Shredded Wheat spoon size

maxcal <- cereal %>% 
    filter(calories == max(calories)) %>% 
    select(name) 
maxcal
#1 Mueslix Crispy Blend

mincal <- cereal %>% 
    filter(calories == min(calories)) %>% 
    select(name) 
mincal
# 1 All-Bran with Extra Fiber
# 2 Puffed Rice              
# 3 Puffed Wheat 

```

# 3. Which cereal is rated the highest? Is there a relationship between rating and any of the nutritional values you explored above?
```{r}

maxrate <- cereal %>% 
    filter(rating == max(rating)) %>% 
    select(name) 
maxrate
#1 All-Bran with Extra Fiber

##correlations##

#make matrix 
my_matrix <- cereal[, c("rating", "sugars", "calories", "protein", "fat")]

#correlations with plots
corr <- pairs.panels(my_matrix)

#correlations with plots
corr <- pairs.panels(my_matrix[c("rating", "sugars", "calories", "protein", "fat")])


```

#4. Which brand has the highest average rating? Is there a significant difference between average ratings across brands?
```{r}

maxrate <- cereal %>% 
    filter(rating == max(rating)) %>% 
    select(brand) 
maxrate

#linear model examining diff between avg ratings across brands

#first quickly examine this var
table(cereal$brand)
#American home food products only has 1 so I'm removing it
cereal <- cereal %>% 
  filter(brand == 'American Home Foood Products') %>% 
  remove()
cereal[cereal$brand == 'American Home Foood Products'] <- NA


#trying some loops and functions that we learned 

#identify unique brands and make a list to call in results
uniq_brands <- unique(cereal$brand)
models_floop <- as.list(rep(NA, length(uniq_brands)))

for (i in 1:(length(uniq_brands))) {
  
  temp <- cereal %>% 
    filter(brand == uniq_brands[i])
  
  models_floop[i] <- lm(cereal$rating ~ 1 + cereal$sugars, data = temp)
}

#function method
brand <- cereal %>% 
  split(.$brand)

foo <- function(x){
  lm(rating ~ 1 + sugars, data =x) %>% 
    return()
}

models <- lapply(brand,foo)

```

